Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-12 Thesis/chapter/01-introduction.tex
First Draft (NO POST-EMMA)

The remainder of this work is organized with section 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background on topics of \gls{pv}, material science and computational science which were used in this work.
In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in \label{sec:res-emma} and further analysis in section \ref{sec:res-post}.
\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}

>>>>

The remainder of this work is organized with section 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background on topics of \gls{pv}, material science and computational science which were used in this work.
In sections \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three subsections: material specific results are presented in section \ref{sec:res-mat}, results regarding \gls{pso} in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
\td{Finally, section \ref{sec:outlook} discusses the outlook and next steps}

### 2022-11-12 Thesis/chapter/05-computational-details.tex
First Draft (NO POST-EMMA)

\subsection{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
each $n=5$ points after and before the origin at least $d=2$ points distance (which boils
down to the values from \SI{0.02}{\volt} to \SI{0.07}{\volt}), 
averaging their V and I values and calculating
\begin{equation}
    g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer and better comparable to the \gls{mse} the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$, calculated in following way:
\begin{equation}
	s_i = \begin{cases}
	1 &\text{if} \quad -log(g_i) < 5 \\
	0 &\text{if} \quad -log(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

>>>>

\subsection{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (aluminium dot) the gradient $g$ at $V=0$ is calculated by taking 
each 5 points before and after the origin with at least 2 points distance (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages of each point cloud $\overline{V}$ and $\overline{I}$ and taking the ratio of differences 
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}.
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer and better comparable to the \gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$, calculated in following way:
\begin{equation}
	s_i = \begin{cases}
	1 &\text{if} \quad -log(g_i) < 5 \\
	0 &\text{if} \quad -log(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

### 2022-11-12 Thesis/chapter/060-results-material.tex
drueber lesen bis excl 04 characterization
First Draft (NO POST-EMMA)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific and Pre-optimization}
%\subsubsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \ch{H2SO4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers there was no clear improvement and the results reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure \ref{fig:sem-old} shows a typical details of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A solution with \gls{acoh} was stable for approximately \td{24h} sealed with Parafilm. 
%192 was first with IPOH
Whereas a solution with \gls{ipo} as stabilizing agent stayed stable for circa \td{72h}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed instead of producing a separate solution for each sample.
It was discovered that after a \gls{acoh} solution has aged beyond cloudiness 
the addition of a small amount of \gls{ipo} can even reversed the aging effect. % for \td{respectable} amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

@@

%%%%%%%%% CROSS SECTION
Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline part which makes up most of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with buthanolic recipe)  can be observed.
%
Measuring the cross section on steel was not as straight forward because of the ductility of steel. 
The only way to get an insight into the thickness of the layer via \gls{sem} was through 
scratching the surface with an diamond glass cutter. 
The result can be seen in figure \ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be around \um{1}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{SEM}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Infra Red}

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{reflectance of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
    \caption{IR} \label{fig:ir}
\end{figure}

In figure \ref{fig:ir-gt} transmission spectra of visible and \gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers the more of the light is absorbed (1000nm) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is the more wavy the graph, which most likely can be attributed to interference.
This trend can also be observed in figure \ref{fig:ir-gr}.
The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
Figure \ref{fig:ir-gr} shows reflectance spectra of visible and \gls{nir} at an incident angle of 45 degrees. 
The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Current Voltage Curves} 
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
        \caption{log good 3x4F} \label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
        \caption{log okay 10x1F} \label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log bad 3x3F} \label{fig:iv-log-bad}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat good 3x4F} \label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
    \end{subfigure}
    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold} \label{fig:iv}
\end{figure}

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of a insulating sample. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section \ref{sec:exp-eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample as in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements from moderate sample. 
Most of the \gls{iv}s have a maximum voltage of under \num{e-6} V, 
but there are some so called pin holes with conductance above this threshold. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of the functions 
is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
but was not investigated further. 
Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating.

@@

Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate, steel, and 
the substrate with ten layers of double concentrated solution (experiment number 6113, see \td{appendix}).
In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108).
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
%This wideness is is due to polycrystalline form of the material which is expected 
%due to the sol-gel creation process and multiple applications of layers. 
%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Preoptimization}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the \gls{db} velocity was too slow (less than \mmps{1}), no layer was formed. 
With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
Additionally, the temperature while \gls{db} affects the resulting layer together with the \gls{db} velocity.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Material Scientific and Pre-optimization}
\label{sec:res-mat}
%\subsubsection{Solution}
%%%%%%%% AQUATIC 
As already indicated in the experimental section the aquatic recipe adopted from Anwar et al.\cite{Anwar2017} failed to produce a homogeneous layer. 
The solution was opaque from the beginning and the resulting layers were patchy and laced with cracks (see figure \ref{fig:sem-old}). 
Altering the ratios of ingredients, adjusting pH (by adding \gls{naoh}, \ch{H2SO4} or \gls{hcl}) or adding \gls{sds} as surfactant didn't improve the resulting \gls{zro} layers. 
% ../../Data/SEM/SEM_2020_11_10_Old_Recipes/10_2L_19.tif
% ../../Data/SEM/SEM_2020_11_19_Old_Recipes/71_SL_NT4_11.tif
Even after the consecutive application of two layers there was no clear improvement and the results reminded rather of a sparse crust than of a film. 
%It is assumed that the solution was far from the optimum for a sol-gel process. 
%
Figure \ref{fig:sem-old} shows a typical detail view of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
%These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks, non coated areas and inhomogeneity were 
%part of (ausmachen) 
shared characteristics among 
all samples created with the aquatic recipe. 
%even after several/multiple/various alteration to the recipe.

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reversed the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

@@

%%%%%%%%% CROSS SECTION
Figure \ref{fig:sem-cs1} shows the cross section of a single layer of \gls{zro} on \gls{fto} glass at a deliberate fracture.
The large crystalline structure which makes up most of the upper part of the image is \gls{fto}. 
The boundary to glass is visible at the very top. 
%On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer can be observed: \gls{zro} produced by buthanolic recipe inspired by Hu et al..
On the lower edge of \gls{fto} a circa 100nm thick homogeneous layer of \gls{zro} (produced with 5 layers of \gls{1f} buthanolic \gls{acoh} recipe)  can be observed.
%
Measuring the cross section on steel was not as straight forward because of the ductility of steel. 
The only way to get an insight into the thickness of the layer via \gls{sem} was through 
scratching the surface with an diamond glass cutter. 
The result can be seen in figure \ref{fig:sem-cs2}. 
5 layers of double concentrated solution were applied to this sample. 
Assuming that the raised structure resembling a tentacle is \gls{zro}, 
the thickness of the layer can be estimated to be around \um{1}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsubsection{SEM}

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Spectrometry}

\begin{figure}[htb]
    \centering
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gt.png}
        \caption{Transmittance of \gls{zro} on glass} \label{fig:ir-gt}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \centering
        \includegraphics[width=.99\textwidth]{Pics/ir-gr.png}
        \caption{Reflectance of \gls{zro} on glass} \label{fig:ir-gr}
    \end{subfigure}
    \caption{\td{UVVisIR}} \label{fig:ir}
\end{figure}

In figure \ref{fig:ir-gt} transmission spectra of \gls{uv}/\gls{vis}/\gls{nir} light can be seen. 
Each sample had different numbers of layers. 
The incident angle was 0 degree for each sample.
%differnt numbers of layers of \gls{zro} on a glass slide with 0 degree incident angle. 
The more layers the more of the light is absorbed (1000nm) by the \gls{zro} layers. 
%The trend is not monotonic due to inhomogenities in the sample???b
The thicker the layer is the more wavy the graph, which most likely can be attributed to interference.
This trend can also be observed in figure \ref{fig:ir-gr}.
The light interference patterns at low wavelengths indicate that the thickness of the film is in the order of magnitude of the wavelengths\cite{delimafilho2017film}. 
Figure \ref{fig:ir-gr} shows reflectance spectra of \gls{uv}/\gls{vis}/\gls{nir} at an incident angle of 45 degrees. 
The shift of the wavy part of the spectra (comparing reflectance with transmittance) 
can be explained by the longer path of light through the \gls{zro} layer because of the incident angle. 
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Current Voltage Curves} 
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
        \caption{log good 3x4F} \label{fig:iv-log-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
        \caption{log okay 10x1F} \label{fig:iv-log-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log bad 3x3F} \label{fig:iv-log-bad}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat good 3x4F} \label{fig:iv-stat-good}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat okay 10x1F} \label{fig:iv-stat-okay}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat bad 3x3F} \label{fig:iv-stat-bad}
    \end{subfigure}
%    \caption{\td{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold}} \label{fig:iv}
    \caption{Current-voltage curves and the distribution of gradients for three representative samples, \td{include $\rho$ threshold}}  
    \label{fig:iv}
\end{figure}

%Figures \ref{fig:iv-log-good} and \ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure \ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure \ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where ordinate shows the logarithm to the base of 10 of the absolute value of the current. 
Each line represents a I-V measurement at a distinct contact applied by sputtering through a mask. 
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and quite a few show hardly any current which is the ideal. 
For each measurement the conductivity (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}). 
Figure \ref{fig:iv-stat-good} shows the distribution of gradients for the same sample depicted in \ref{fig:iv-log-good}.
%
Figures \ref{fig:iv-log-okay} and \ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures \ref{fig:iv-log-good} and \ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin. 
This deviation is similar to the deviation because of the photo-currents\cite{perez2018solar}, 
but was not investigated further. 
Though, the photo-current is compelling, it is most likely not zutreffend because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
%
Finally, figures \ref{fig:iv-log-bad} and \ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
%
\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}

@@

Figure \ref{fig:xrd} shows \gls{xrd} spectra of the substrate (steel) and 
the substrate with ten layers of double concentrated solution (\gls{emma} experiment number 6113, see Appendix \ref{sec:app-emma}).
In addition two idealized spectra from the Crystallography Open Database of cubic \gls{zro} (COD ID 1521753\cite{gkatz1971xray}) and of $\alpha$-Fe (COD ID 1100108) are depicted.
The four largest peaks of cubic \gls{zro} at $\theta=30, 51, 60, 35$ clearly stand out against the noise from the experimental spectrum. %can be clearly seen in the experimental spectra.
\td{why cubic \gls{zro} when cubic stable above 2270C? todo: find xrd of monoclinic and tetragonal}
%In figure \ref{fig:xrd} the two strongest $\alpha$-Fe peaks can be seen clearly. 
%The highest peak of \gls{zro} is very \td{broadened} and is therefore not as distinct. 
%This wideness is is due to polycrystalline form of the material which is expected 
%due to the sol-gel creation process and multiple applications of layers. 
%Nonetheless, the \gls{xrd} spectra shows clearly that the produced layer is \gls{zro}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Preoptimization}
Before the optimization with the \gls{emma} algorithm, 
the boundaries of the input variables were explored. 
Especially, the \gls{db} velocity $v_{DB}$ (i.e. the velocity with which the blade moves and spreads the solution over the sample)
was varied and examined during pre-optimization. 
The slower the \gls{db} velocity, the more uniformly the solution evaporated. 
If the $v_{DB}$ was too slow (less than \mmps{1}), no layer was formed. 
With the reason that the force exerted by the blade on the liquid not being strong enough to overcome surface tension. 
This means that behind the blade a meniscus would pull the liquid without leaving any for the gelling process. 
Additionally, the temperature while \gls{db} $T_{DB}$ affects the evaporation process together with the \gls{db} velocity $v_{DB}$.
